Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-17 motivation.tex
fix grammar

With the current international tensions regarding enrichment capabilities, this
work aims to measure the effectiveness of an enrichment cascade when used outside of
its designed scope and quantify the attractiveness of such way to build up
significant quantity of \gls{HEU}.

>>>>

With the current international tensions regarding enrichment capabilities, this
work aims to measure the effectiveness of a symmetric enrichment cascade when
used outside of its designed scope and quantify the attractiveness of such way
to build up significant quantity of \gls{HEU}.

### 2018-07-17 theory.tex
fix grammar

The cascade is built as a ideal symmetric cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ represent the feed to product and the feed to
tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

>>>>

The cascade is built as a symmetric ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ represent the feed to product and the feed to
tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}
